Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-03 article.rnw
shuffled one more sentence
Interchange the dashing and dotting of the lines on the histogram.
The dotted green line was hard to read (a combination of the pale green
and the small dots). Both green dashes and red dots are easy enough to see.

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dotted", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dashed", col="red")
	@
	\end{subfigure}

	\caption{%
		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
		The dotted green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
		The dashed red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
	}
	\label{fig:ic}
\end{figure}
% DBS: Reconsider green and red to be more colour-blind friendly. I've already changed it so that the lines are different types.

@@

The structure of the coclassification matrices was very different in the row groups than in the column groups.
That is, most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.
A Mantel test of the coclassification matrix for the rows against that for the columns showed that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).

@@

Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).

% DBS: But the fact that the labels say effects and responses reminds me of a lingering "doubt" I had when reading the main text. We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects. As long as we're consistent, I'm fine either way. But we need to remember we're writing the paper for the audience and not for ourselves. ;)

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="red")
	@
	\end{subfigure}

	\caption{%
		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
		The dotted red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
	}
	\label{fig:ic}
\end{figure}
% DBS: Reconsider green and red to be more colour-blind friendly. I've already changed it so that the lines are different types.

@@

The structure of the coclassification matrices was very different in the row groups than in the column groups.
That is, most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.
A Mantel test of the coclassification matrix for the rows against that for the columns showed that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).

@@

% DBS: But the fact that the labels in figure 3 say effects and responses reminds me of a lingering "doubt" I had when reading the main text. We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects. As long as we're consistent, I'm fine either way. But we need to remember we're writing the paper for the audience and not for ourselves. ;)
